Mapping stellar surfaces\\ III: A Bayesian Approach to Doppler Imaging

### 2021-10-05 src/ms.tex
foo

%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/gp.pdf}
        \caption{%
            Samples from a spectral-spatial-temporal Gaussian Process.
        }
        \label{fig:gp}
    \end{centering}
\end{figure}
%

>>>>

\subsection{A Spectral-Spatial-Temporal Gaussian Process}
\label{sec:discussion:gp}

%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/gp.pdf}
        \caption{%
            Ten samples from a spectral-spatial-temporal Gaussian Process constructed from the algorithm presented here.
            Each panel shows a different sample, each of which consists of ten epochs, offset vertically for visibility.
            The rest frame spectrum is the same as in Figure~\ref{fig:spot_setup} and the star is inclined at $i = 40^\circ$ with equatorial velocity $v = 50{,}000$ km/s.
            The star is assumed to have spots with radius $r = 15^\circ$, ten percent contrast, and active latitude $\phi = 30^\circ \pm 5^\circ$.
        }
        \label{fig:gp}
    \end{centering}
\end{figure}
%
